---
title: "My first paper with Rmarkdown"
author: "Claudio Fronterrè"
date: "19 July 2018"
output:
  pdf_document: default
  odt_document: default
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis

During this practical I will be using the `iris` dataset in R.  

```{r summary}
summary(iris$Sepal.Length)
mean(iris$Sepal.Length)
```

I can also include inline R code. The average sepal length is `r round(mean(iris$Sepal.Length), 2)`. 

## Including Plots

It is extremely easy to include plots. 

```{r plot1, echo=FALSE}
plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width")
```

To add a caption it is enough to specify the `fig.cap` argument in the R chunk header.

```{r plot2, echo=FALSE, fig.cap="Scatterplot of sepal length and sepal width."}
plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width")
```

You can change the height and widht and decide to align the figure in a different way.

```{r plot3, echo=FALSE, fig.cap="Scatterplot of sepal length and sepal width.", fig.height=3, fig.width=4, fig.align='right'}
plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width")
```

You can also plot two figure side by side.

```{r plot4, echo=FALSE, fig.show='hold', out.width="50%"}
plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", ylab = "Sepal Width")
plot(iris$Petal.Length, iris$Petal.Width, xlab = "Petal Length", ylab = "Petal Width")
```

## Including tables

To generate well formatted tables you can use the `kable` function from the `knitr` package. An extensive list of features can be found [here](http://haozhu233.github.io/kableExtra/). 

```{r table1, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)

table <- iris %>% 
  group_by(Species) %>% 
  summarise(Mean = mean(Petal.Length), Sd = sd(Petal.Length))

knitr::kable(table)
```

Let's customise our table a little bit.

```{r table2, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(table, digits = 2, col.names = c("Species", "Petal Mean", "Petal Sd"), 
             caption = "Summary table.", align = "lcc")
```

Adding the output from a model as a table.

```{r table3, echo=FALSE, results='asis', message=FALSE}
fit <- lm(Sepal.Length ~ Sepal.Width, data = iris)
options(xtable.comment = FALSE)
xtable::xtable(fit)
```

# Math equations

Inline LaTeX equations can be written in a pair of dollar signs using the LaTeX syntax, e.g. $f(x)=x^2$. Math expressions of the display style can be written in a pair of double dollar signs, e.g. 

$$Y_i=\alpha + \beta X_i + \epsilon_i$$

# Citations

@Lee2013-zb shows that .... [@Lee2013-zb]. More about bibliography and citations can be found [here](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

# Refrences